\documentclass{article}
\usepackage{listings}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{courier}

\lstdefinestyle{Bash}
{language=bash,
basicstyle=\ttfamily\footnotesize,
backgroundcolor=\color{gray!20},
breaklines=true,
breakatwhitespace=true
}


\begin{document}

\title{{TJBatchExtractor}}
\author{Kyle Miller}

\maketitle

\section{Introduction}
This document describes the {TJBatchExtractor} project. This project is
a regular expression based information extractor designed to operate on
text captured from female escort advertisements originating from {US}
sections of {B}ackpage.com. The motivation is to extract domain specific
information that may be informative in identifying individuals or groups
responsible for each advertisement. To that end, the information extracted
focuses on physical description and contact information.

The project is built upon {GATE} ({G}eneral {A}rchitecure for {T}ext
{E}ngineering) produced by the {U}niversity of {S}heffield. {GATE} is
available at 
\begin{lstlisting}[style=Bash]
https://gate.ac.uk.
\end{lstlisting}
All necessary dependencies for the 
{TJBatchExtractor} projects are contained within this repository. It should
not be necessary to download {GATE}. {GATE} may be useful however, if one
wishes to modify this project an/or make use of the {GUI} and performance
analysis machinery {GATE} provides.

In the context of {GATE} applications, there are a few key phrases for which
knowing the definitions may prove helpful. These are given below.

\begin{description}
\item[Language Resource] A document or collection of documents (corpus)
\item[Processing Resource] A self contained program designed to consume and produce/modify annotations on text
\item[Application] A collection of processing resources arranged in a pipeline
\item[JAPE] A regular expression language that operates on annotations
\item[Gazetteer] A look up table that produces annotations
\end{description}

\section{Components}

The {TJBatchExtractor} project consists of the following components.

\subsection{{TJBatchExtractor.java}}

The java program {TJBatchExtractor.java} is a wrapper for the {GATE}
application called {TJinformationExtractor}. It's function is to wrap
{TJinformationExtractor} in such a way that it can load a text document and
process many advertisements in parallel, finally writing the results to
a csv file upon completion. {TJBatchExtractor.java} expects a single text
file to be provided as input on which each line represents the text associated
with an advertisement. Thus, it is necessary to remove line breaks from ad text.
The program writes its results to a user specified file, "Out.csv" by default.

To compile: 
\begin{lstlisting}[style=Bash]
$ javac -classpath '.:/dependencies/*' TJBatchExtractor.java
\end{lstlisting}

To run:
\begin{lstlisting}[style=Bash]
$ java -classpath '.:/dependencies/*' TJBatchExtractor [num_threads] [textfile] [outfile]
\end{lstlisting}

\subsubsection{Outfile}

The following is a description of the features extracted,
their definitions, and notes about notation. Many features
may be multi-valued (e.g. names, phone numbers). 
In such cases, the output file uses ';' to 
delimit values within ',' delimited fields.

It should be noted that many of these features have not been
normalized. So, for example, blond and blonde may both 
appear as hair colors, despite having the same interpretation.


\begin{description}
\item[Perspective\_1st] Count of 1st person pronouns
\item[Perspective\_3rd] Count of 3rd person pronouns
\item[Name] Female first names
\item[Age] Age
\item[Cost] Dollar figure charged for various services. Notation is given as Dollar/Measure/Unit. Dollar represents a cost, Unit represents object of the cost (e.g. hours, minutes, short stay, special, etc.), Measure represents the number of units (e.g. 30 minutes, 1 hour, hhr, etc.)
\item[Height\_ft] Height in feet, multiple values correlate with multiple values of Height\_in
\item[Height\_in] Remaining inches of height, correlates with Height\_ft
\item[Weight] Weight in lbs
\item[Cup] Cup size
\item[Chest] Chest measurement
\item[Waist] Waist measurement
\item[Hip] Hip measurement
\item[Ethnicity] Country referenced ethnicity (e.g. Spanish, Russian, etc.)
\item[SkinColor] Color of skin
\item[EyeColor] Color of eyes
\item[HairColor] Color of hair
\item[Restriction\_Type] One of [no, over]; the type of restriction, i.e. "no black men", or "only men over 45."
\item[Restriction\_Ethnicity] The ethnicity/ skin color restricted
\item[Restriction\_Age] The threshold age value for the over restrictions
\item[PhoneNumber] Phone number
\item[AreaCode\_State] State associated with phone number's area code
\item[AreaCode\_Cities] Cities/ locations associated with phone number's area code
\item[Email] Email address
\item[Url] urls specifically referenced or linked to in the body
\item[Media] iframes and other foreign sourced content
\end{description}

\section{{TJinformationExtractor}}

{TJinformationExtractor} is a {GATE} application, the definition of which is
stored in 
\begin{lstlisting}[style=Bash]
/TJInfoExtractor/application.xgapp.
\end{lstlisting} The xgapp file may be loaded directly into {GATE} by selecting
"{Restore Application from File...}" allowing one to make use of the {GATE} interface.

This pipeline makes use of 
the {ANNIE} {E}nglish {T}okeniser that ships with {GATE}, two custom processing
resources {I}nteger\_{T}agger and {P}hone\_{N}umber\_{T}agger, an {ANNIE} {G}azetteer,
and {JAPE}-{P}lus transducer. The application begins by tokenizing the text. It then
identifies all token/sequences of tokens that could be interpreted as an integer. Next, it
identifies phone numbers ({US} and {C}anada). Finally, it identifies other features
and attempts to resolve conflicts. Note that the entire application has been configured to 
be case insensitive.

\subsection{{Integer Tagger}}
The integer tagger is a processing resource that identifies references to integers
in noisy (possibly obfuscated) text. The source can be found in 
\begin{lstlisting}[style=Bash]
/TJInfoExtractor/plugins/Tagger_Integer/src/gate/creole/integers/.
\end{lstlisting} It produces the "Integer" annotation. Each integer
annotation indicates the type ("numbers", "words", or "wordsAndNumbers"), numeric value, and
whether any leading zeros are present. 

The resource can be set to respect token boundaries (set to false in this application), 
sentence boundaries (set to false in this application, requires the use of a sentence splitter prior
to integer tagger in the pipeline), and dictionary entries (set to true in this application). If set to true, {respectTokenBoundaries} 
prevents the resource from annotating a set of characters that cross
token boundaries as an integer. If set to true, {respectSentenceBoundaries} prevents the resource
from annotating a set of characters that cross sentence boundaries as an integer. If set to true, respectDictionaryEntries 
prevents the resource from annotating characters that are contained within a token that appears in the dictionary as an integer. 
For example, "one" in will be tagged as an integer in "some one" but not in "a cone." 

The resource makes use of dictionaries of integer characters, symbols, and dictionary words. These files are located in
\begin{lstlisting}[style=Bash]
/TJInfoExtractor/plugins/Tagger_Integer/resources/languages/.
\end{lstlisting} Standard numerical symbols 0-9 are hard coded into the resource.

\subsection{{Phone Number Tagger}}
The phone number tagger is a processing resource that identifies references to US and Canadian
phone numbers. The source can be found in 
\begin{lstlisting}[style=Bash]
/TJInfoExtractor/plugins/Tagger_PhoneNumber/src/gate/creole/phonenumbers/.
\end{lstlisting} The resource 
can be configured to find both 10 digit and 7 digit phone numbers (both true by default). The tagger can also
be configured to respect sentence boundaries as described above (set to false in this application).

The resource produces the "{PhoneNumber}" annotation including the state, region, and value associated to a phone number.
This resource finds groups of integers, annotated by the integer tagger, that are separated by no more than
two word tokens (as indicated by the tokenizer). Note, an unlimited amount of punctuation may separate integers and 
they will still be grouped together. Each group of numbers is then analyzed for subgroups of size 7, 10, or 11 that have the
following properties. 11 digit groups must begin with 1. The area code in 10 and 11 digit groups must be valid according to
an area code dictionary located in 
\begin{lstlisting}[style=Bash]
/TJInfoExtractor/plugins/Tagger_PhoneNumber/resources/.
\end{lstlisting} For all groups the prefix (first 
three digits following the area code) must not begin with a 1 nor end in 11.

Finally, for larger groups of digits, phone numbers are tagged in a left first greedy fashion modulated by preferences on digit subgrouping.
In this context, digits are considered in the same subgroup if there are no non-white space tokens between them. 10 and 11 digit phone numbers are preferred over 7 digit numbers.
11 digit numbers are treated as 10 digit numbers, ignoring the first digit. For 10 digit numbers preference is given to subgrouping sizes according to the following order
3-3-4, 10, 1-1-1-1-1-1-1-1-1-1, *-3-4, 3-7, 3-*, 6-4, *, where * indicates arbitrary digit subgroupings. For 7 digit numbers digit numbers, digit subgrouping sizes must be 
one of the following (in order of preference) 3-4, 7, 1-1-1-1-1-1-1.

\subsection{{ANNIE Gazetteer}}

The gazetteer lists can be found in 
\begin{lstlisting}[style=Bash]
/TJInfoExtractror/application-resources/TJ_Gazetteer/.
\end{lstlisting} This gazetteer resource
contains look up tables for prefixes, key words, and suffixes associated to the features of interest (e.g. colors, hair, eyes,
names, cup size, etc.). Occurrences of these tokens are annotated for use by the {JAPE} transducer.

\subsection{{JAPE-Plus Transducer}}

{JAPE} is a regular expression language for {GATE} that operates over annotations. The {JAPE} transducer creates or 
modifies annotations based on matches to rule patterns. The jape files containing the {JAPE} rules for this application
are contained in 
\begin{lstlisting}[style=Bash]
/TJInfoExtractor/application-resources/jape_transducers/.
\end{lstlisting}
Each rule file is run in the order specified in {TJ\_Annotation.jape}. These rules try to match common linguistic patterns
employed when mentioning each feature. Ultimately they are responsible for creating the feature annotations as well as resolving
conflicts between annotations. 

\section{Performance}
Below are performance measures for the features extracted, measured on
1000 randomly selected ads, adjudicated by hand.

Features that have sub-features such as height, cost, and restrictions, are
evaluated on match of all sub-features for the purposes of this evaluation.
Also, note that here the age feature is evaluated only on age mentions in the body of
an add. While it is common to indicate age in the ad title, this extractor was specifically
constructed to operate on the body.

\begin{description}
\item[Prevalence] The count of feature occurrence/ number of ads
\item[Correct] The count of feature occurrences correctly extracted
\item[Partial] The count of feature occurrences extracted, albeit incorrectly
\item[Missing] The count of feature occurrences missed (i.e. false negatives)
\item[False pos] The count of falsely identified occurrences
\end{description}

\begin{small}
\begin{center}
\begin{tabular}{l c c c c c c c c}
Feature & Prevalence & Correct & Partial & Missing & False Pos & Recall & Precision & F-measure \\ \hline
Age        & 0.067  & 49   &   0   &    18   &   1   &      0.731 &  0.980  &    0.838  \\
Cost       & 0.55   & 489  &   0   &    61   &   17  &      0.889 &  0.966  &    0.926 \\
Email      & 0.012  & 12   &   0   &    0    &   0   &      1.000 &  1.000  &    1.000 \\
Ethnicity  & 0.29   & 254  &   0   &    36   &   8   &      0.876 &  0.969  &    0.920 \\
EyeColor   & 0.106  & 102  &   0   &    4    &   0   &      0.962 &  1.000  &    0.981 \\ 
HairColor  & 0.266  & 255  &   4   &    7    &   1   &      0.959 &  0.981  &    0.970 \\
Name       & 0.993  & 795  &   7   &    191  &   85  &      0.801 &  0.896  &    0.846 \\
PhoneNumber & 1.077 & 1072 &   2   &    3    &   0   &      0.995 &  0.998  &    0.997 \\
Restriction & 0.069 & 56   &   2   &    11   &   1   &      0.812 &  0.949  &    0.875 \\
SkinColor  & 0.105  & 102  &   0   &    3    &   3   &      0.971 &  0.971  &    0.971 \\
Url        & 0.047  & 41   &   5   &    1    &   2   &      0.872 &  0.854  &    0.863 \\
Height     & 0.236  & 227  &   3   &    6    &   2   &      0.962 &  0.978  &    0.970 \\
Measurement & 0.206 & 182  &   16  &    8    &   0   &      0.883 &  0.919  &    0.901 \\
Weight     & 0.182  & 166  &   4   &    12   &   0   &      0.912 &  0.976  &    0.943 \\
\end{tabular}
\end{center}
\end{small}

\end{document}